Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-07 Response to reviewers.tex

\begin{verbatim}
In all our experiments we have applied  WEKA's implementation 
of the ReliefF algorithm in the regression problems. 
This version is called "Regressional ReliefF" or "RReliefF" for 
short, which was first introduced and implemented by Robnik-Sikonja 
and Kononenko (in ref. [73] for numeric targets). 
Therefore, we have clarified this point in the text to remove 
any ambiguity.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph) 
\begin{verbatim}
For CSF, estimating the correlation between attributes is 
standard linear (Pearson's) correlation. The details have 
been added to the text to clarify this point.
\end{verbatim}
% Antonio - TODO: say where is this clarification in the text (page/paragraph)

~\\
\noindent (2) \emph{In sub-section 4.2, five methods are introduced, i.e.,M5P,kNN,RF,LR and SVM. In sub-section 5.1, why is MLP (multi-layer perceptron) with one hidden layer described ?}

\begin{verbatim}
The current paper includes in sub-section 
`2.1. Selecting an appropriate forecasting method' (former
sub-section 4.2) six methods: M5P, kNN, RF, LR, SVM, MLP,
 and ELM (requested by Reviewer #2).

Moreover, as suggested by the Reviewer #2 (see his/her first comment), 
the results obtained with the two last methods have been included in 
this new version of the paper.
\end{verbatim}
% Antonio - TODO: say where are these results (table/figure/page)
% [pedro] TODO => decir que se han añadido ciertas refs sobre ELM

@@

~\\
\noindent (3) \emph{As we known, tree-based methods (e.g., M5P and RF) themselves embed feature selection procedure. That is, some features are chosen to build trees. It is not fair enough to compare five methods in Table 3. }

\begin{verbatim}
Although we agree with the reviewer's comment, and the RF and M5P 
have an embedded feature selection mechanism, we believe that it 
is unfair to compare them with the filter based feature selection 
methods we have deployed in our research. 
The aim is simply to show to the decision maker what are the possible 
results when we apply one of the off-the-shelf classifiers available 
in a common open source framework such as WEKA. 
Moreover, it is not uncommon in the literature to see such comparison 
between classifiers, as in the paper:
  M. Fernandez-Delgado, E. Cernadas, S. Barro, and D. Amorim. 2014. 
  Do we need hundreds of classifiers to solve real world 
  classification problems?. J. Mach. Learn. Res. 15, 1, pp.3133-3181
which incorporates a general comparison between all these classifiers.
\end{verbatim}
%Every response should end with changes made in the paper, even if it
%is only clarification. It is not an invitation to discussion. 
% Antonio - TODO: say how this has been addressed in the paper (where it is clarified). Say if this reference has been included as new.

~\\
\noindent (4) \emph{It seems more reasonable to organize and write that paper according to regression viewpoint only. }

\begin{verbatim}
The reviewer is right, thus, we have revised the whole paper referring 
to the term `regression' instead of `classification'. 
In addition, some sections have been renamed, such as subsection 2.1, 
in order to better suit the regression viewpoint.
Moreover this have been also addressed solving the issue related 
to comment #1, where the application procedure of feature selection 
methods for regression problems has been clarified. 
\end{verbatim}
% Antonio - CONCERN: I'm a bit afraid about the term 'organize' which I don't know if has been addressed in any way in the new version...
% [Pedro] you are right... but the way the reviewer has expressed it is quite strange.
% [Hossam]: Regarding your first concern, the reviewer asked for organizing and writing not reorganizing, so we have just addressed that by emphasizing the term regression in all the paper and we have clarified how we applied the FS methods customized for regression problems. So I think we addressed this issue adequately.

@@

~\\
\noindent (5) \emph{It is necessary to write that paper more concisely. }

\begin{verbatim}
Following reviewer's suggestion we have reorganized some parts of the 
text and several paragraphs have been rewritten in order to make 
them shorter, clearer and to improve its comprehension 
(i.e. paragraph XX in page YY, and paragraph XX in page YY).

Also, several tables have been moved to the Appendix and that
data has been presented now as the new Figures XX, YY, ZZ.

@@

~\\
\noindent (2) \emph{The authors should clarify their main contributions in the introduction parts.}

\begin{verbatim}
We have rewritten the introduction and included this new text:

"Our main contribution is, thus, to develop a methodology to 
process book sales data in order to first find out relevant 
variables and then use these variables to process data so that 
the publisher, using them, can estimate sales and from them order 
a specific print run, instead of standard ones, which are around 
300 copies for standard books and around 5000 for those that are 
considered, in advance, best sellers."

Also, in the next-to-last paragraph, we have laid out our 
methodology and clarified the main contributions of this paper 
to the state of the art.
\end{verbatim}
% Antonio - TODO: I rewritten this text, so we should copy the new one here. But I think we all should contribute to create a very good justification (see next CONCERN). :D
% Antonio - CONCERN: We should definitely write a convincing text which separates this work from existing approaches. Maybe the use of real data is a good point. And also emphasize the contribution to the SotA.
% [Pedro] well, no previous work on "print run & book sales prediction" has been done (at least, I have not found anything in the bibliography)
% [Hossam] about the contribution, I agree with you. We can mention that we used real data in our work.

@@

~\\
\noindent (3) \emph{Technologies related to recommend systems may have the ability to deal with this problem. The authors should add the recommend systems into the future work part. }

\begin{verbatim}
Taking into account the reviewer's comment, the recommendation 
systems have been added to the future work section, at the end 
of Section 7 (see page XX).
\end{verbatim}
% Antonio - TODO: put the correct page when the text is finished

~\\
\noindent (4) \emph{Some tables should be transfer to figures because there are too many tables. }

\begin{verbatim}
Following reviewer's suggestion, several tables have been moved to 
the Appendix and that data has been summarized and presented 
as the new Figures XX, YY, ZZ in order to make that numeric data clearer 
and to improve their comprehension.
\end{verbatim}
% Antonio - CONCERN: I think we should move ALL the results tables and include a couple of figures more. Please see my e-mail on this respect. ;)
% Antonio - TODO: Talk about the final tables and figures.
% Let's talk about them!   :)

@@

\begin{verbatim}
Taking into account the reviewer's comment, we have improved the 
description of the methodology including a flowchart (see Figure XX 
at page YY).
\end{verbatim}
% Antonio - CONCERN: I don't know if te reviewer is speaking about the whole methodology or just about the regression/forecasting part... The figure shows a rough summary of the methodology.
% Antonio - TODO: Improve the figure, which is a bit 'generic'. Put the correct figure and page.
% Almost every paper I have read (and that has been cited in the SotA) shows a very generic flowchat

~\\
\noindent (4) \emph{In Section 5, parameter settings of 
M5P, kNN and RF also should be shown. }

\begin{verbatim}
We have improved Section 5, including the parameter settings of 
M5P, kNN and RF methods (see paragraph XX at page YY).

The authors want to express our gratitude to this reviewer 
for his/her suggestions.
\end{verbatim}
% Antonio - CONCERN: don't we also put the configuration of the rest of the methods? And say it. :D 
% Could we use a table for showing them easily?
% [pedro] TODO: design the table taken the parameters/values shown in section 5.1
% Antonio - TODO: say paragraph/page where they are.

### 2016-09-07 paper.tex
solving some TODOs

% Antonio - TODO: The next paragraph is referring to Section 2.1. We must change it.
% Why? anyway, I add "As stated before,"
As stated before, in Section \ref{subsec:select_method} a selection of the best 
forecasting techniques that have been conducted has been reported, looking for 
those rule- or tree-based, together with numerical methods which could yield 
the best results.

>>>>

As stated before, in Section \ref{subsec:select_method}, a selection of the best 
forecasting techniques has been reported, looking for those rule- or tree-based, 
together with numerical regression methods which could yield the best results.
